### 2020-04-20 README.Rmd
Fixed the link to the repository in README.md

Please note that this paper is prepared as a reproducible research document. The source R Markdown document, as well as all data and code needed to reproduce/review/extend the analysis can be obtained from the following anonymous Drive folder:

https://drive.google.com/open?id=1d_40N_QXo2Fl14r3T3CHs84IED-B1rV_

>>>>

Please note that this paper is prepared as a reproducible research document. The source R Markdown document, as well as all data and code needed to reproduce/review/extend the analysis can be obtained from the following link (this repository):

https://github.com/paezha/covid19-environmental-correlates/tree/master/Environmental-Correlates-of-COVID19-Spain
